Exploring the Impact of Queer Media Characters on LGBTQ+ Psychological Well-Being: The Role of Queer Media Consumption, Perceived Authenticity, and Intersectionality

### 2025-02-10 Manuscript.qmd
Update lit review
Update current study and hypo

Some studies have also criticized that queer media characters presenting stereotypes could be harmful to the LGBTQ+ community. @yaksich_consuming_2005 and @guidotto_cashing_2006 indicated that many queer media representations are the commodification of the LGBTQ+ community. The queer media monopoly of ‘perfect homo’ (i.e., flamboyant Caucasian and middle-classed gay men) neglects intersectionality, reinforcing the LGBTQ+ stereotypes in the audience’s perceptions. @nolke_making_2018 identified the intersectional invisibility of queer media representations by applying intersectional analysis of a series of advertisements from 2009 to 2015. The discussion from this study also indicated that the hegemony of queer stereotypes and the lack of intersectionality could be harmful to the LGBTQ+ community by bringing them lower confidence and mental illnesses (e.g., depressive disorders).

>>>>

Some studies have also criticized that queer media characters presenting stereotypes could be harmful to the LGBTQ+ community. @yaksich_consuming_2005 and @guidotto_cashing_2006 indicated that many queer media representations are the commodification of the LGBTQ+ community. The queer media monopoly of ‘perfect homo’ (i.e., flamboyant Caucasian and middle-classed gay men) neglects intersectionality, reinforcing the LGBTQ+ stereotypes in the audience’s perceptions. @nolke_making_2018 identified the intersectional invisibility of queer media representations by applying intersectional analysis of a series of advertisements from 2009 to 2015. The discussion from this study also indicated that the hegemony of queer stereotypes and the lack of intersectionality could be harmful to the LGBTQ+ community by bringing them lower confidence and mental illnesses (e.g., depressive disorders).
Nevertheless, no established instrument has systematically compared how LGBTQ+ perceived queer character authenticity (i.e., free of stereotypes) or perceived queer character intersectionality could impact their psychological well-being, calling for more scholarly intention to relevant measurement.

# Current Study and Hypotheses

The current study examined queer media characters’ impacts on LGBTQ+ individuals’ psychological well-being through two overarching research questions. The first research question investigated whether there were differences in queer characters’ psychological impacts among LGBTQ+ individuals with different identities. Specifically, this study has compared LGBTQ+ individuals with different sexual orientations, gender identities, races, ages, and nationalities on queer characters’ psychological impacts. Given the fact that there were still queer stereotypes and fewer intersectional representations in mass media, the current study stated that queer media characters’ positive impacts on psychological well-being would be weaker for LGBTQ+ individuals with more invisible and marginalized identities (e.g., asexual, transgender, black, elder generations, developing countries’ residents) while being stronger for those with more visible identities (e.g., gay, cisgender, white, younger generations, developed countries’ residents). The second research question asked whether queer media consumption patterns, perceived character authenticity, and perceived character intersectionality can predict queer media characters’ psychological impacts. Specifically, this study hypothesized that lower ratings for perceived character authenticity and intersectionality would result in lower ratings for queer characters’ positive psychological impacts. Conversely, higher ratings for perceived character authenticity and intersectionality would result in higher ratings for queer characters’ positive psychological impacts.
